Untitled

### 2024-03-13 writing/paper.Rmd
adding theme for the plots
adding task in the begining

@@

>>>>

theme_set(theme_light())

@@

# change the names of the vars in the tables
# put larger tables in portrait mode
# add literature to the ND var subsections
# talk about the descriptives of the data
# interpret the results 
# finalize the citations 
# discuss (the disposability test, generalization problem, more dimensions to add, time, student vs school level issue of aggregation)
